### 2016-03-30 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some more uniformity in figure + text

The measurement of \glspl{FRF} of dynamic systems is an important topic in the measurement society.
\gls{FRF} measurement techniques are discussed, for instance, in
\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to real practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
This capability is very useful for model validation and/or model selection~\citep{Pintelon2012}.

This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e. no user interaction. Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{Bendat1993,Oppenheim1983}. 
Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. Note that a more general discussion on the \gls{LPM}, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.

@@

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise, the null hypothesis states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  In particular, the null hypothesis is rejected when the empirical $F$ statistic is small, i.e.
  \begin{equation}
    F \isdef \frac{s^2(i-1)}{s^2(i)} \leq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
  \end{equation}
  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom.
  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.

@@

  \item This procedure is repeated until a segment $\segm{\hat{g}}{i-1}$ is found that is dominated by the actual impulse response according to the outcome of the $F$-test and the absolute \gls{RMS} value of the segment.
  At that point, it is very likely that the transition from noise to the actual impulse response happens within the segment $\segm{\hat{g}}{i-1}$.
  One now has the choice to accept the last sample of $\segm{\hat{g}}{i-1}$ to be the last meaningful sample $\truncTime$ for the impulse response.
  The accuracy of this estimate is limited by the length of the segment $L_S$.

  \item
  A more accurate estimate can be obtained by dividing the segment $\segm{\hat{g}}{i-1}$ -- which may contain both the signal and noise -- yet again into smaller segments. The procedure described above is then repeated until a satisfactory, accurate $\truncTime$ is obtained, or until the subsegments have a length that is too short ($L_{S\min} = 10$) to guarantee the accuracy of the RMS values. %rely on the RMS values to be accurate.
  To start this refinement, the last $\segm{\hat{g}}{i}$ should be used to compare the RMS with the $F$-test, since the last subsegment of $\segm{\hat{g}}{i-1}$ cannot be asserted to be dominated by noise.

\end{enumerate}
This procedure is illustrated in \figref{fig:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
y(t)       &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
% \eqref{eq:systemSimulations}. 
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smooth estimate.  %after which all samples are fixed to a zero value for the smoothed estimate.

@@

\item
Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
\begin{align}\label{eq:truncTimeExpFit}
t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
\end{align}
where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below. %(see the discussion below).
% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.

\item
 Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.

@@

\begin{figure}[tbh] %top bottom here
\centering
\setlength\figurewidth{0.85\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/expfit.tikz}
\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response via the fit of  an exponential. 
The light gray line is the noisy impulse response, and the dark gray one is its absolute value. 
Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}. 
Black thick line: estimated exponential function \eqref{eq:expFit}.}
\TODO{describe marker again!}
\label{FRF_truncate_expfitter}
\end{figure}

@@

The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
The result is depicted in \figref{FRF_truncate_expfitter}. An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line). The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e. $\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).

@@

In \figref{fig:pdfAndRMSeVStruncTime}, the black graph is the \gls{RMS} error of the estimated \gls{FRF} (without the \gls{DC} value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated. Its minimum is indicated by a black dot, to the left of which a steep increase is observed. 
This is due to a bias error. 
To the right hand side of the minimum, the \gls{RMS} error increases very gradually, due to an increase of the noise variance.

@@

The truncation time is determined from the data as described in \secref{sec:nonparametric:truncation:exponentialfit}. This was done on $1000$ realizations of the noise, and depicted in \figref{fig:pdfAndRMSeVStruncTime} by the histogram.
Clearly, both methoda for selecting the truncation time $\truncTime$ have a good overall performance, based on the mode of its distribution (around the $90^{\text{th}}$ sample).

@@

From the plot, we can conclude that the \gls{RMSE} increases rapidly when $\truncTime$ is smaller than the optimal.
On the other hand, selection of a value of $\truncTime$ that is too large, is not nearly as detrimental to the modeling error.
The graph also shows that the \gls{RMSE} of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied. Also, one observes a low sensitivity of the \gls{RMSE} w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum. 
Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.

@@

@@

\TODO{write about boxcar average, add reference}
\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/expFitBoxAverager.tikz}
         \caption{Exponential fit of a boxcar averager}
\end{figure}

>>>>

This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
The advantage of using the nonparametric models is basically that the `models` often are very simple and hence require little user interaction to construct.
Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors~\citep{Bendat1993,Oppenheim1983,Schoukens2006LPM}. 
Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. 
Note that a more general discussion on the \gls{LPM}, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.

@@

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise (or assumed to be noise if $i=N_S$), the null hypothesis effectively states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  In particular, the null hypothesis is rejected when the empirical $F$ statistic is small, i.e.
  \begin{equation}
    F \isdef \frac{s^2(i-1)}{s^2(i)} \leq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
  \end{equation}
  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom.
  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.

@@

  \item This procedure is repeated until a segment $\segm{\hat{g}}{\starred{i}-1}$ is found that is dominated by the actual impulse response according to the outcome of the $F$-test and the absolute \gls{RMS} value of the segment.
  At that point, it is very likely that the transition from noise to the actual impulse response happens within the segment $\segm{\hat{g}}{\starred{i}-1}$.
  One now has the choice to accept the last sample of $\segm{\hat{g}}{\starred{i}-1}$ to be the last meaningful sample $\truncTime$ for the impulse response.
  The accuracy of this estimate is limited by the length of the segment $L_S$.

  \item
  A more accurate estimate can be obtained by dividing the segment $\segm{\hat{g}}{\starred{i}-1}$ -- which may contain both the signal and noise -- yet again into smaller segments.
  The procedure described above is then repeated until a satisfactory, accurate $\truncTime$ is obtained, or until the subsegments have a length that is too short ($L_{S\min} = 10$) to guarantee the accuracy of the RMS values. %rely on the RMS values to be accurate.
  To start this refinement, the last $\segm{\hat{g}}{\starred{i}}$ should be used to compare the RMS with the $F$-test, since the last subsegment of $\segm{\hat{g}}{\starred{i}-1}$ cannot be asserted to be dominated by noise.

\end{enumerate}
This procedure is illustrated in \figref{fig:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
y(t)       &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
% \eqref{eq:systemSimulations}. 
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smoothed \gls{FRF} estimate.

@@

\item
Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
\begin{align}\label{eq:truncTimeExpFit}
\truncTime = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
\end{align}
where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below. %(see the discussion below).
% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.

\item
 Truncate the estimated impulse response for $t \geqslant \truncTime$.

@@

\begin{figure}[tbh] %top bottom here
\centering
\setlength\figurewidth{0.85\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/expfit.tikz}
\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response $g(t)$ via the fit of  an exponential through the peaks of $\abs{g(t)}$ that are above $5\noiseStd$ with $\noiseStd$ is the estimated noise level, as per \eqref{eq:TmaxDef}.}
\label{fig:nonparametric:trunc:impresp:expfit}
\end{figure}

@@

The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
The result is depicted in \figref{fig:nonparametric:trunc:impresp:expfit}. 
An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line). The truncation time (black vertical line) $\truncTime$ was selected as the time instant at which the fitted exponential fell below $0.4\noiseStd$ (i.e. $\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).

@@

In \figref{fig:pdfAndRMSeVStruncTime}, the black graph is the \gls{RMS} error of the estimated \gls{FRF} (without the \gls{DC} value) as a function of the time $\truncTime$ at which the impulse response is truncated. 
To the left of the optimal truncation length, the \gls{RMS} error increases steeply.
In that region, one is essentially using a overly simplified impulse response to represent the system and hence the \gls{RMS} error is dominated by the bias error.
To the right hand side of the minimum, the \gls{RMS} error increases more gradually, due to an increase of the noise variance.

@@

The truncation time is determined from the data as described in \secref{sec:nonparametric:truncation:exponentialfit}. 
This was done on $1000$ realizations of the noise, and depicted in \figref{fig:pdfAndRMSeVStruncTime} by the histogram.
Clearly, both methods for selecting the truncation time $\truncTime$ have a good overall performance, based on the mode of their distribution (around the $90^{\text{th}}$ sample).

@@

From the plot, we can conclude that the \gls{RMSE} increases rapidly when $\truncTime$ is smaller than the optimal.
On the other hand, selection of a value of $\truncTime$ that is too large, is not nearly as detrimental to the modeling error.
The graph also shows that the \gls{RMSE} of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied. Also, one observes a low sensitivity of the \gls{RMSE} w.r.t.~$\truncTime$, when truncating at times beyond that optimum. 
Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.

@@

The different methods to determine $\truncTime$ presented in this section, essentially enforce different prior knowledge of the impulse response of the system.
The exponential fitting technique relies on the exponential decay present in most physical systems.
The $F$-test based technique is better suited for systems where a sudden jump in the impulse response is present.

@@

\TODO{write about boxcar average, add reference}
\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/expFitBoxAverager.tikz}
         \caption{Exponential fit of the impulse response of a  boxcar averager.}
\end{figure}

### 2016-03-30 ch03-lrm/lrm-paper.tex
Fix mathbold stuff
Some small things
Some more uniformity in figure + text

\TODO{
\begin{itemize}
    \item choice $s$ or $z$
    \item bounds RMSE, Bias, StdDev
    \item derivation Bias
    \item comparison LPM/LRM
      \begin{itemize}
        \item Good LPM window
        \item Good LRM window
      \end{itemize}
    \item influence of noise filter: mismatch with model
    \item comparison LRM/LRik (LBTLS)
\end{itemize}
}

@@

Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:design-matrix} easily leads to ill-conditioned systems, additional measures are taken to improve numerical conditioning.
To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G,eq:LRM:model:T}
\begin{equation}
\dw{r}{k} \isdef \frac{\omega_{k+r} - \omega_k}{\Delta \omega_k}
\label{eq:freqScaling}
\end{equation}
where
\begin{equation}
  \Delta \omega_k \isdef
  \max
  \Set{
    \abs{ \omega_k - \omega_j} |  \vphantom{\frac{a}{b}}  \omega_j \in \LocalWindow[k]
  }
\end{equation}
such that $\abs{\dw{r}{k}} \leq 1$ when $r \in \LocalShifts{k}$.

@@

To determine the bias, an approach similar to \citep[Appendix A]{Guillaume1995} is followed.
Let us denote the expected value of the cost function over all measurements $\LocalVector{Z}$ as
\begin{align}
  \ELSCost{\theta}
              & \isdef 
                   \E[\LocalVector{Z}]%
                         {    
                                \LSCost{\LocalVector{\theta}, \LocalVector{Z}}} \\
              & = \ELSCost[0]{\theta} + \ELSCost[n]{\theta} \\
    \ELSCost[0]{\theta} & \isdef 
            \frac{1}{F} 
                \sum_{r} 
                     \left| 
                             \LocalModel{A}(r, \LocalVector{\theta}) \true{\LocalVector{Y}}
                          - \LocalModel{B}(r, \LocalVector{\theta}) \true{\LocalVector{U}}
                          - \LocalModel{C}(r, \LocalVector{\theta}) 
                    \right|^2 \\
    \ELSCost[n]{\theta} & \isdef 
              \frac{1}{F} 
                     \sum_{r} 
                              \left| \LocalModel{A}(r,\LocalVector{\theta}) \right|^2 
                              \sigma_V^2
\end{align}
Note that this function is a quadratic function of $\LocalVector{\theta}$ and hence it can be represented exactly by its second order Taylor series around $\true\theta$:
\begin{multline}
  \ELSCost{\theta} = \ELSCost{\true\theta} 
  + \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  \left( \theta - \true\theta \right)\\
  + \frac{1}{2} \left( \theta - \true\theta \right)^{\T} 
  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
   \left( \theta - \true\theta \right)
   \text{.}
\end{multline}
The minimizer $\estim\theta$ of this function can be obtained by equating the derivative
\begin{equation}
  \PartialDerivative{\ELSCost{\estim\theta}}{\estim\theta} = \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T} + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
   \left( \estim\theta - \true\theta \right)
\end{equation}
to zero.
This is equivalent to 
\begin{equation}
  \left( \estim\theta - \true\theta \right) = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T}
  \text{.}
\end{equation}
which expresses the bias $\Delta\theta = \left( \estim\theta - \true\theta \right)$ of the estimated parameters.
Since $\ELSCost[0]{\theta}$ is minimized in $\true\theta$, this simplifies to
\begin{equation}
  \Delta\theta = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
  \text{.}
\end{equation}

@@

\paragraph{Leave-out cross-validation}
Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
In effect, such an approach calculates the \gls{PRESS} for each local model:
\begin{equation}
 \PRESS = \frac{1}{2N_W+1} \sum_{r=-N_W}^{N_W} 
                          \abs{\ignoring{r}{\LocalVector{e}}}^2
                          \text{,}
\label{eq:PRESS-general}
\end{equation}
where $\ignoring{r}{\LocalVector{e}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\hat{Y}}}$, i.e. the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
The model with the smallest \gls{PRESS} is retained.
In general, this means that \gls{LOOCV} requires estimating $2N_W + 1$ additional models (one for each omitted data point) and hence can be very time-consuming.

>>>>

\begin{itemize}
    \item \TODO{choice $s$ or $z$}
    \item \TODO{bounds RMSE, Bias, StdDev}
    \item \TODO{derivation Bias}
    \item \TODO{comparison LPM/LRM}
      \begin{itemize}
        \item \TODO{Good LPM window}
        \item \TODO{Good LRM window}
      \end{itemize}
    \item \TODO{influence of noise filter: mismatch with model}
    \item \TODO{comparison LRM/LRik (LBTLS)}
\end{itemize}

@@

Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:design-matrix} easily leads to ill-conditioned systems, additional measures are taken to improve numerical conditioning.
To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}
\begin{equation}
\dw{r}{k} \isdef \frac{\omega_{k+r} - \omega_k}{\Delta \omega_k}
\label{eq:freqScaling}
\end{equation}
where
\begin{equation}
  \Delta \omega_k \isdef
  \max
  \Set{
    \abs{ \omega_k - \omega_j} |  \vphantom{\frac{a}{b}}  \omega_j \in \LocalWindow[k]
  }
\end{equation}
such that $\abs{\dw{r}{k}} \leq 1$ when $r \in \LocalShifts{k}$.

@@

To determine the bias, an approach similar to \citep[Appendix A]{Guillaume1995} is followed.
Let us denote the expected value of the cost function over all measurements $\LocalVector{Z}$ as
\begin{align}
  \ELSCost{\theta}
              & \isdef 
                   \E[\LocalVector{Z}]%
                         {    
                                \LSCost{\LocalVector{\theta}, \LocalVector{Z}}} \\
              & = \ELSCost[0]{\theta} + \ELSCost[n]{\theta} \\
    \ELSCost[0]{\theta} & \isdef 
            \frac{1}{F} 
                \sum_{r} 
                     \left| 
                             \LocalModel{A}(r, \LocalVector{\theta}) \true{\LocalVector{Y}}
                          - \LocalModel{B}(r, \LocalVector{\theta}) \true{\LocalVector{U}}
                          - \LocalModel{C}(r, \LocalVector{\theta}) 
                    \right|^2 \\
    \ELSCost[n]{\theta} & \isdef 
              \frac{1}{F} 
                     \sum_{r} 
                              \left| \LocalModel{A}(r,\LocalVector{\theta}) \right|^2 
                              \sigma_V^2
\end{align}
Note that this function is a quadratic function of $\LocalVector{\theta}$ and hence it can be represented exactly by its second order Taylor series around $\true\theta$:
\begin{multline}
  \ELSCost{\theta} = \ELSCost{\true\theta} 
  + \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  \left( \theta - \true\theta \right) %\\
  + \frac{1}{2} \left( \theta - \true\theta \right)^{\T} 
  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
   \left( \theta - \true\theta \right)
   \text{.}
\end{multline}
The minimizer $\estim\theta$ of this function can be obtained by equating the derivative
\begin{equation}
  \PartialDerivative{\ELSCost{\estim\theta}}{\estim\theta} = \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T} + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
   \left( \estim\theta - \true\theta \right)
\end{equation}
to zero.
This is equivalent to 
\begin{equation}
  \left( \estim\theta - \true\theta \right) = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T}
  \text{.}
\end{equation}
which expresses the bias $\Delta\theta = \left( \estim\theta - \true\theta \right)$ of the estimated parameters.
Since $\ELSCost[0]{\theta}$ is minimized in $\true\theta$, this simplifies to
\begin{equation}
  \Delta\theta = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
  \text{.}
\end{equation}

@@

\paragraph{Leave-out cross-validation}
Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
In effect, such an approach calculates the \gls{PRESS} for each local model:
\begin{equation}
 \PRESS = \frac{1}{2N_W+1} \sum_{r=-N_W}^{N_W} 
                          \abs{\ignoring{r}{\LocalVector{e}}}^2
                          \text{,}
\label{eq:PRESS-general}
\end{equation}
where $\ignoring{r}{\LocalVector{e}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e. the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
The model with the smallest \gls{PRESS} is retained.
In general, this means that \gls{LOOCV} requires estimating $2N_W + 1$ additional models (one for each omitted data point) and hence can be very time-consuming.

### 2016-03-30 ch03-lrm/nonparametric.tex
Remove epigraph from Milgram
Address some TODOs
Different figure names per chapter
Import LRM-paper draft
Some small things
Some more uniformity in figure + text

\chapter{Non-parametric modeling}
\def\thisDir{ch03-lrm}
\label{sec:nonparametric}

\myEpigraph{The essence in obedience consists in the fact that a person comes to view himself as an instrument for carrying out another person's wishes and he therefore no longer regards himself as responsible for his actions.}{Stanley Milgram}{Obedience to Authority}

\section{\TODO{LPM}}
\section{\TODO{LRM}}
\TODO{import LRM paper}
\section{\TODO{LPM with impulse response truncation}}
\input{\thisDir/LPMSmooth_ML_EG_JS_JL.tex}

@@

\subsubsection{\TODO{AVIS}}
\subsubsection{\TODO{F16}}

>>>>

\chapter{Non-parametric modeling}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\label{sec:nonparametric}

\section{Introduction}
\label{sec:nonparametric:introduction}

Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have recently received new research interest from the community.

\begin{itemize}
\item \TODO{explain non-parametric}
\item \TODO{explain why non-parametric is good}
\end{itemize}

The measurement of \glspl{FRF} of dynamic systems is an important step in many technical applications, often used as a simple visualization of the system dynamics.
\gls{FRF} measurement techniques are discussed, for instance, in
\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
This capability is very useful for model validation and/or model selection~\citep{Pintelon2012}.

\section{\TODO{LPM}}
\section{\TODO{LRM}}
\input{\thisDir/lrm-paper.tex}

\section{LPM with impulse response truncation}
\input{\thisDir/LPMSmooth_ML_EG_JS_JL.tex}

@@

\subsubsection{\TODO{AVIS}}
% \subsubsection{\TODO{F16}}
